\documentclass[12pt]{article}

\usepackage{shellesc}

\usepackage[a4paper,width=160mm,top=30mm,bottom=20mm,headheight=10mm]{geometry}

\usepackage{fancyhdr}

%\usepackage{biblatex}
\usepackage[square,numbers]{natbib}
%\addbibresource{references.bib}
\bibliographystyle{abbrvnat}

\usepackage{graphicx}
\graphicspath{ {./images/} }

\usepackage{siunitx}

\usepackage{placeins}

\usepackage{csquotes}

\usepackage{enumitem}

\usepackage{algorithm}
\usepackage{algpseudocode}

%%% Tikz 
\usepackage{tikz}
\usepackage{pgfplots}\pgfplotsset{compat=1.18}
%\usepackage{pgfplotstable}
\usepackage{pgfmath}
\usetikzlibrary{arrows.meta,positioning,calc,intersections,external,shapes,angles,patterns,quotes}
\usepgfplotslibrary{units, groupplots, statistics, colormaps}

\usepgfplotslibrary{external}
\tikzexternalize
\tikzsetexternalprefix{figures/}
%\tikzset{external/force remake}
%\tikzset{external/remake next}

\newcommand{\inserttikzfig}[1]{
\tikzsetnextfilename{#1}%image name
\input{#1}}

\usepackage{amsmath} % for the equation* environment
\usepackage{amsfonts}
\usepackage{amssymb}

\usepackage{caption}
\usepackage{subcaption}

\usepackage{hyperref}

\usepackage{cleveref}

\crefname{figure}{figure}{figures}
\Crefname{figure}{Figure}{Figures}
\crefname{equation}{equation}{equations}
\Crefname{equation}{Equation}{Equations}

\newcommand{\mytitle}{Neuromorphic control of embodied central pattern generators : Errata}
\newcommand{\mysubtitle}{A bio-inspired approach to motion}
\newcommand{\myname}{Christian Fernandez Lorden}
\newcommand{\mychaptername}{Undefined}
\newcommand{\mychapterdesignation}{Chapter}
\newcommand{\mychapter}[1]{\chapter{#1}\renewcommand{\mychaptername}{\mychapterdesignation~\thechapter : #1}}

\pagestyle{fancy}
\fancyhead{}
\fancyhead[L]{}
\fancyfoot{}
\fancyfoot[C]{}
%\fancyfoot[CO,CE]{\myname}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\fancypagestyle{plain}{%
    \fancyhead{}
    \fancyfoot{}
    \fancyfoot[C]{}
    %\fancyfoot[CO,CE]{\myname}
    \renewcommand{\headrulewidth}{0pt}
    \renewcommand{\footrulewidth}{0pt}
}

\hypersetup{% PDF METADATA
    pdfinfo={%
    Title={\mytitle},%
    Author={\myname},%
    Subject={Neuromorphic Engineering},%
    Producer={LuaLaTeX with hyperref and pgfplots},%
    Creator={\myname},%
    Keywords={Neuron, Control, Pendulum, Neuromodulation, Engineering, Bursting, Spiking, CPG},%
    },%
    %keeppdfinfo 
}%

\usepackage[normalem]{ulem}

\allowdisplaybreaks % Allow equation to page break

\usepackage{titling}
\setlength{\droptitle}{-3cm}

\title{\mytitle}
\author{\myname}



\begin{document}
    \maketitle
    
    \begin{description}
        \item[1: p. 1] End of the first paragraph of the page. Change \enquote{\textelp{} and autonomy \sout{and} increasing \textelp{}} to \enquote{\textelp{} and autonomy, increasing \textelp{}}.
        
        \item[2: p. 11] End of the penultimate paragraph of section 2.5. Missing references. Change \enquote{\textelp{} (citation needed).} to \enquote{\textelp{} \citep{errata1,errata2,errata3}.}. Reference numbers are not adjusted to the thesis bibliography.
        
        \item[3: p. 12] First paragraph of section 3.1. Change \enquote{\textelp{} the model \sout{I} used \textelp{}} to \enquote{\textelp{} the model used \textelp{}}.
        
        \item[4: p. 16] Third paragraph of the page. Change \enquote{Yet,Franci et al. \textelp{}} to \enquote{Yet, Franci et al. \textelp{}}.
        
        \item[5: p. 30] First paragraph of section 4.2. Change \enquote{\textelp{} the bursting neuron is the heart \textelp{}} to \enquote{\textelp{} the bursting neuron is at the heart \textelp{}}.
        
        \item[6: p.33] Second paragraph of section 4.3. Change \enquote{Figure 4.5 displays \textelp{}} to \enquote{Figure 4.6 displays \textelp{}}.
        
        \item[7: p.40] Middle of the second paragraph of the page. Change \enquote{The difference can be explained easily when considering the \sout{equalization} that \textelp{}} to \enquote{The difference can be explained easily when considering the equations that \textelp{}}.
        
        \item[8: p.40] End of the second paragraph of the page. Change \enquote{Thus, mixed feedback can be abstracted as equation (4.3) plus one, \textelp{}} to \enquote{Thus, mixed feedback can be abstracted as equation (4.4) plus one, \textelp{}}.
        
        \item[9: p.67] Start of the third paragraph of the page. Change \enquote{Figure 5.5 graph of the \textelp{}} to \enquote{In figure 5.5, the graph of the \textelp{}}.
        
        \item[10: p.73] End of the second paragraph of section 6.2 change \enquote{\textelp{} control of the pendulum primed the realization \textelp{}} to \enquote{\textelp{} control of the pendulum outweighed the realization \textelp{}}.
        
        \item[11: p.80] First paragraph of the page. Change \enquote{The model was modified to a second motor \textelp{}} to \enquote{The model was modified to add a second motor \textelp{}}.
    \end{description} 

    
    \bibliography{references}
\end{document}


 
